PineAPPL:\\ EW and mixed QCD--EW corrections for PDF fits

### 2020-08-05 paper/sec-pineappl.tex

Note that in this section we have omitted the dependence of the weights $w$, the observable $\mathcal{O}$, and the scales $\mu_\mathrm{F}, \mu_\mathrm{R}, Q^2$ on the specific kinematics for which they are computed.
Indeed, beyond LO, different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva}, for example, they are labelled with an index $\alpha$, see eq.~(12) therein).
In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC} maximally one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this is not the general case.
In Catani--Seymour subtraction~\cite{Catani:1996jh}, for example, different dipoles have different phase spaces and therefore different scales.
However, \textsc{PineAPPL} remains completely blind to this fact, and a consistent treatment is ensured by correctly using the interface between \textsc{PineAPPL}, which fills each event into a grid using the \emph{numerical value} of $Q^2$.

>>>>

Note that in this section we have omitted the dependence of the weights $w$, the observable $\mathcal{O}$, and the scales $\mu_\mathrm{F}, \mu_\mathrm{R}, Q^2$ on the specific kinematics for which they are computed.
Indeed, beyond LO, different kinematic contributions have to be considered (in ref.~\cite{Bertone:2014zva}, for example, they are labelled with an index $\alpha$, see eq.~(12) therein).
In the FKS subtraction scheme~\cite{Frixione:1995ms,Frixione:1997np} employed in \textsc{mg5\_aMC} maximally one type of kinematics for each counterterm (soft, collinear, and soft-collinear) is needed, but this is not the general case.
In Catani--Seymour subtraction~\cite{Catani:1996jh,Catani:2002hc}, for example, different dipoles have different phase spaces and therefore different scales.
However, \textsc{PineAPPL} remains completely blind to this fact, and a consistent treatment is ensured by correctly using the interface between \textsc{PineAPPL}, which fills each event into a grid using the \emph{numerical value} of $Q^2$.
